\documentclass{article}
\usepackage{color}
\usepackage[a4paper, margin = 1 in]{geometry}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{colorlinks = true,
    urlcolor=blue}

\begin{document}

\title{\Huge \textbf{Blake Byer} \vspace{-1.25em}}

\author{\\
    \href{mailto:blake.byer@uky.edu}{blake.byer@uky.edu} \\
    \href{https://linkedin.com/in/blake-byer}{linkedin.com/in/blake-byer} \\
    \href{https://github.com/blakebyer}{github.com/blakebyer}
}
\date{\today}
\maketitle

\pagenumbering{arabic}
\begin{flushleft}

\section*{Education}

{\large Bachelor of Science in Neuroscience \vspace{0.5em}}\hfill December 2025

\textit{University of Kentucky}

\textit{Minor in Computer Science}

\textit{With Honors, 3.95 GPA}

\section*{Experience}

\subsection*{SURE Scholar {\hfill\normalsize\normalfont\ June 2024 -- August 2024}}
\textit{University of North Carolina at Chapel-Hill \vspace{0.5em}}

SURE Scholar at the University of North Carolina at Chapel-Hill. I studied rare lysosomal storage disease patients
and their COVID-19 outcomes in the National COVID Cohort Collaborative (N3C).

\subsection*{Research Assistant {\hfill\normalsize\normalfont\ August 2023 -- Present}}
\textit{University of Kentucky \vspace{0.5em}}

Research Assistant at the University of Kentucky College of Medicine. I research polygenic risk scores for 
Alzheimer's disease and statistical fine-mapping for GWAS loci prioritization.

\subsection*{Research Assistant {\hfill\normalsize\normalfont\ January 2023 -- August 2023}}
\textit{University of Kentucky \vspace{0.5em}}

Research Assistant at the Sports Medicine Research Institute at the University of Kentucky College of Health Sciences. 
I contributed to a pilot study that tested wireless motion capture and force-plate insoles for gait retraining of military
personnel. 

\section*{Presentations}
\subsection*{Office of Graduate Education Symposium {\hfill\normalsize\normalfont\ July 2024}}
\textit{University of North Carolina at Chapel-Hill}

Lysosomal storage diseases may be protective against severe COVID-19 infection. Clustering analysis shows that lung disease and lysosomal storage diseases further increase 
infection severity. \href{https://doi.org/10.5281/zenodo.12971921}{10.5281/zenodo.12971921}

\subsection*{Great Lakes Bioinformatics Conference {\hfill\normalsize\normalfont\ May 2024}}
\textit{University of Pittsburgh \vspace{0.5em}}

Averaging polygenic risk scores derived from multiple genome-wide association studies increases predictive accuracy for Alzheimer’s disease.

\section*{Selected Publications}
\begin{enumerate}
\item Averaging polygenic risk scores derived from multiple genome-wide association studies increases predictive accuracy for Alzheimer’s disease. Manuscript in preparation.
\item Lysosomal storage diseases and COVID-19. Manuscript in preparation.
\end{enumerate}

\section*{Awards}
\begin{itemize}
\item Great Lakes Bioinformatics Conference Travel Fellowship, International Society for Computational Biology, 2024
\item Eagle Scout Award, Boy Scouts of America, 2019
\item \href{https://gazettetimes.com/news/local/boy-scouts-who-helped-troop-leader-to-safety-win-youth-hero-award/article_bf6fda77-1873-59c3-880e-4f05c45d1ef5.html}{Bob and Billie Holcomb Youth Hero Award, Benton Community Foundation, 2017}
\end{itemize}

\section*{Memberships}
\begin{itemize}
\item International Society for Computational Biology, 2024 - Present
\end{itemize}

\end{flushleft}

\end{document}


